\documentclass[line,margin]{res}
    \usepackage[none]{hyphenat}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \begin{document}
\name{{\LARGE Fedor Paretsky}}
\address{me@f3d0r.com | (206) 372-8476 | Seattle, Wa | f3d0r.com}
\begin{resume}
	\vspace{-5mm}
	        
	
	\section{Education}
	\textbf{University of Washington}, {\sl BS in Applied Physics (Technical) and Mathematics} GPA: 3.6\hfill Sep. 2016 | Jun. 2020\\Seattle, WA\\\\
	\textbf{Garfield High School}, {\sl High School Degree} GPA: 3.7\hfill Sep. 2012 | Jun. 2016\\Seattle, WA
	\section{EXPERIENCE}
	\textbf{aspace, Inc.}, {\sl Co-Founder/CEO}\hfill Oct. 2015 | Present\\Seattle, WA\\\begin{itemize} \itemsep 3pt
	\item Building an app/sensor infra. that uses live data to connect commuters to cheap, remote parking spots, using last-mile transit to get to destination.
	\item Y Combinator 2018 Startup School (YC SS18)
	\end{itemize}
	\textbf{srnd.org (StudentRND)}, {\sl Code Evangelist®}\hfill May 2016 | Present\\U.S.A.\\\begin{itemize} \itemsep 3pt
	\item A StudentRND Code Evangelist® goes out into the world to spread a love of code with StudentRND, a non-profit getting students excited and involved in Computer Science. Code Evangelists are Day-Of coordinators, assisting with various event logistics at it\textquotesingle{}s events and by MCing and individually interacting with students during SRND\textquotesingle{}s events, like CodeDay.
	\end{itemize}
	\textbf{University of Washington Housing \& Food Services}, {\sl Resident Advisor (RA)}\hfill Sep. 2017 | Mar. 2018\\Seattle, WA\\\begin{itemize} \itemsep 3pt
	\item Resident Advisors (RAs) work in the University of Washington residence halls to establish a cohesive and responsible community in their designated area, model and support issues related to diversity, facilitate the holistic development of residents through programming, promote resident involvement, and refer, advise, and support residents as they deal with academic and personal issues.
	\end{itemize}
	\textbf{Metrix:Create Space}, {\sl Lead Intern}\hfill Feb. 2016 | Sep. 2016\\Seattle, WA\\\begin{itemize} \itemsep 3pt
	\item Manage and maintain hacker space
	\item Repaired and refurbished professional/industrial-grade machinery
	\item Assisted with completion of customer orders
	\end{itemize}
	\section{SKILLS}
	\begin{tabular}{@{}ll}
		\textbf{Programming Languages}: & Java, Kotlin, Python, JavaScript, node.js, Arduino, Lua, Swift \\
		\textbf{Web Frameworks}:        & Nginx, Apache, Express, web.py                                 \\
		\textbf{Databases}:             & MySQL, NoSQL, Realm, Firebase                                  \\
	\end{tabular}
	\section{PROJECTS}
	\textbf{aspace}, {\sl Java, Kotlin, Python, JavaScript, node.js, Arduino, Lua, Swift}\\ My startup code base, please enquire in-person or by email for more information.\\ https://trya.space\\\\
	\textbf{HQ Trivia Bot}, {\sl Xcode, RESTful APIs}\\ HQ Trivia Bot (not to be used on live games) - PRIVATE repository, please contact for access.\\ https://github.com/f3d0r\\\\
	\section{AWARDS}
	\textbf{Garfield High School Certificate of Excellence in Business Technology and Computer Science}, {\sl Garfield High School Career and Technology Education (CTE) Department} \hfill June 2016 \\
	Awarded to 3 students annually in graduating class. \\\\
	\textbf{Washington State Honors Award}, {\sl Randy Dorn - State Superintendent of Public Instruction} \hfill June 2016 \\
	\\\\
	\textbf{Outstanding Soloist - Honorable Mention}, {\sl Wynton Marsalis} \hfill May 2016 \\
	Awarded at the 2016 International Essentially Ellington Jazz Band Competition. \\\\
	\textbf{Outstanding Soloist}, {\sl Wynton Marsalis} \hfill May 2015 \\
	Awarded at the 2015 International Essentially Ellington Jazz Band Competition. \\\\
	\ 
\end{resume}
\end{document}