%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}

    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Fedor}{Paretsky}{me@fedor.me | (206) 372-8476 | Seattle, WA | fedor.me}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\runsubsection{University of Washington}\descript{| BS Applied Physics and Mathematics}\hfill \location{Seattle, WA | Sep. 2016 - Jun. 2020}\\
    
\sectionsep
  

\runsubsection{Garfield High School}\descript{| High School Degree}\hfill \location{Seattle, WA | Sep. 2012 - Jun. 2016}\\
    
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Newfront Insurance}\descript{| SWE Intern}\hfill \location{newfrontinsurance.com - San Francisco, CA | Jun. 2019 – Present}
\begin{tightemize}
	\item Working with modern TypeScript, Go, Next.js, and Heroku technologies
	\item Converting backend and frontend interfacing technologies to Apollo GraphQL
\end{tightemize}
\sectionsep
\runsubsection{aspace, Inc.}\descript{| Co-Founder/CEO}\hfill \location{trya.space - Seattle, WA | May 2018 – Nov. 2018}
\begin{tightemize}
	\item Built an app/sensor infra. that uses live data to connect commuters to cheap, remote parking spots, using last-mile transit to get to destination.
	\item Created infrastructures for Machine-learning parking behavior, optimized routes with parking vacancy variables, created hardware sensors for detecting parking spot vacancy, built Android and iOS apps, and accompanying backend
	\item Y Combinator W19 Interview and Y Combinator 2018 Startup School (YC SS18)
\end{tightemize}
\sectionsep
\runsubsection{srnd.org (StudentRND)}\descript{| Code Evangelist®}\hfill \location{srnd.org - U.S.A. | May 2016 – Nov. 2018}
\begin{tightemize}
	\item A StudentRND Code Evangelist® goes out into the world to spread a love of code with StudentRND, a non-profit getting students excited and involved in CS. Code Evangelists are day-of coordinators, assisting with various event logistics.
\end{tightemize}
\sectionsep
\runsubsection{University of Washington Housing \& Food Services}\descript{| Resident Advisor (RA)}\hfill \location{Seattle, WA | Sep. 2017 – Mar. 2018}
\begin{tightemize}
	\item Resident Advisors (RAs) work in the UW residence halls to establish a cohesive and responsible community in their designated area, model and support issues related to diversity, and refer, advise, and support residents.
\end{tightemize}
\sectionsep
\runsubsection{Metrix:Create Space}\descript{| Lead Intern}\hfill \location{metrixcreatespace.com - Seattle, WA | Feb. 2016 – Sep. 2016}
\begin{tightemize}
	\item Maintained hacker space and repaired/refurbished professional/industrial-grade machinery
	\item Technologies used: Large- and small-scale 3D printers, industrial laser cutters and PCB printers, CNCs
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
	\descript{Programming Languages}     & {\location{Java, Python, JavaScript, HTML/CSS, node.js, Arduino, Lua}} \\
	\descript{Web Frameworks}            & {\location{Nginx, Apache, Express, web.py}}                            \\
	\descript{Databases}                 & {\location{MySQL, NoSQL, Realm, Firebase}}                             \\
	\descript{Cloud Computing Platforms} & {\location{DigitalOcean, Amazon Web Services, Google Cloud Platform}}  \\
	\descript{Mobile Development}        & {\location{Android (Java), iOS (Swift)}}                               \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\raggedright

\runsubsection{\large{UW Hyperloop}}
\descript{| TypeScript, Ballerina, Drone, Arduino, C++, Go, Python}\hfill \location{https://hyperloop.io}\\
Controls and Powers on the UW Hyperloop Competition Team (participated in 2019 SpaceX Pod Competition).\\
\sectionsep
  

\runsubsection{\large{ssh.uno}}
\descript{| node.js (Electron.js), HTML/CSS/JavaScript, SH}\hfill \location{https://ssh.uno}\\
The fastest, simplest, most intuitive command-line experience yet.\\
\sectionsep
  

\runsubsection{\large{aspace}}
\descript{| node.js, Python, Java, Swift, OSRM Infrastructure, Lua, Arduino}\hfill \location{http://bit.ly/aspacerepo}\\
    
\sectionsep
  

\runsubsection{\large{HQ Trivia Bot}}
\descript{| Swift, RESTful APIs}\hfill \location{https://github.com/f3d0r/triviabot}\\
A HQ Trivia Bot, for educational purposes only.\\
\sectionsep
  

\runsubsection{\large{Deep Learning Playground}}
\descript{| HTML/CSS/JS, Python/Keras, node.js}\hfill \location{http://bit.ly/dlplayground}\\
A Scratch-like interface for creating Keras applications.\\
\sectionsep

\ 
\end{document}